\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-12 response.tex

The simulation result, shown in Fig.4b, displays reachability regions as black ellipsoids, demonstrating empty intersections with Zones 2 and 3. Explicit constraints between reachability regions and obstacles are not activated, assuming basic obstacle avoidance capabilities in robots. The intersections between obstacles and ellipsoids, as observed between agent 3 and Zone 1, are deemed tolerable. All constraints are satisfied, and agents have effectively spread across the map for optimal exploration tasks.

1) Limitations:
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems. {\news However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths. For example, agent 3 in~Fig.4b requires additional security measures to create secured reachability areas. Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~Fig.2b and Fig.4b. The introduction of security constraints resulted in the top left corner remaining unexplored by any robots. This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments. These challenges are further addressed in Section III, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}

\begin{cmt}{}{}
	p 8 - A heuristic approach is provided (Algorithm 1); Is it
	almost impossible for the reader to decipher this algorithm without any
	explanations in words.
\re	We have re-written the algorithm with more detailed and add illustration figure to improve readability and make the approach easier to follow.
\end{cmt}
\rv  
\begin{algorithm}
	\caption{Checkpoint Graph Initialization for Team $\cI_p$}\label{alg:graph}
	{\news \begin{algorithmic}[1]
	\State \textbf{Initialization:} Set $t_{0} \leftarrow 0$ and $t_{2} \leftarrow T$, and add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$ as \emph{start} and \emph{end vertices}.
	\While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
		\State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$. Once found, add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
		\State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
		\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Once found, add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
		\State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
	\EndWhile
	\end{algorithmic}}
	\end{algorithm}
	\setcounter{figure}{4}
	\begin{figure}[H]
		\centering
		\subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_1-v2}}
		\subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_2-v2}}
		\caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
	\end{figure}

\begin{cmt}{}{}
	Similar to the comment above, it will be good to introduce what the
“network multi-flow problem” is.
\re 
We have added additional content to introduce what the "network multi-flow problem" in our setup.
\end{cmt}
\rv 
\textbf{In Section III.A, we make the following modification}

\new{We assume that the planned trajectory for each sub-team has a robot operating on it. The co-observation planning problem is then transformed into a network multi-flow problem by modeling the additional robots as flows traveling through $G$. These flows either follow the planned trajectory via trajectory edges $E_t$ or switch teams via cross-trajectory edges $E_c$ to ensure valid and secured paths. Additionally, they are required to visit every checkpoint $V_p$ to meet the security requirements introduced in~\ref{rmk:checkpoints}. This formulation reduces the co-observation problem to finding valid flow patterns in $G$. The problem is then formulated into linear objectives and constraints, enabling the use of Mixed-Integer Linear Programming (MILP) techniques to efficiently compute feasible solutions. }

\begin{cmt}{}{}
	p3 - “rotation derived from a modifie version of Householder
transformations [25].” ; At least a brief introduction of
Householder transformations (in words) must be included for readers who
are not familiar with it.
\re A brief introduction of Householder transformation is added.
\end{cmt}
\rv \textbf{In Section II.D we modified:}

\new{the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see Appendix B for details).}

\begin{cmt}{}{}
This reachability ellipsoid is an over approximation of the exact
reachability region in Definition 3.”; A proof or at least a
reference to the proof should be provided.
\re While we believe that a formal proof is not necessary for this context, we have added additional content to make the approximation more intuitive. This includes a clearer explanation of how the reachability ellipsoid relates to the exact reachability region. These additions aim to enhance the reader's understanding without requiring formal proof.
\end{cmt}
\setcounter{definition}{1}
\rv {\news
\begin{definition}\label{sec:ellipsoidal definition}
Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
\end{definition}

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }
\begin{cmt}{}{}
	Other grammar related comments.
	\re We have carefully reviewed and corrected all listed grammar mistakes, as well as others that were not explicitly mentioned. 
\end{cmt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 2
\newpage
\section{Response to reviewer 2}

%%%%%%%%%%%%% Comment 2.1
\begin{cmt*}{}{}
	This paper proposed a novel multi-robot optimal planning algorithm that
	integrated mutual observations and introduced reachability constraints
	for enhanced security, which ensures that, even with adversarial
	movements, compromised robots cannot breach forbidden regions without
	missing scheduled co-observations. The contribution of this paper is
	hard evaluate due to the organization. 
	\re We sincerely thank the reviewer for their valuable comments and feedback. We acknowledge the concern regarding the organization of the manuscript, which may have made it challenging to fully evaluate the contributions. In the revised version, we have carefully restructured the manuscript to improve its organization and readability, ensuring that the key contributions are presented more clearly and effectively. We greatly appreciate your valuable feedback, which has been instrumental in enhancing the quality of our work.
\end{cmt*}
%%%%%%%%%%%%% Comment 2.1
\begin{cmt}{}{}
The dimension of p is erroneously defined;
\re After carefully reviewing the manuscript, we believe the reviewer might have meant the dimension of $q$ rather than $p$. In the revised version, we have corrected the definition of $q$ to ensure clarity and accuracy. Thank you for bringing this to our attention.
\end{cmt}
\rv \textbf{In Section II, first paragraph, we modified}

{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation. }

@@

%%%%%%%%%%%%% Comment 2.3
\begin{cmt}{}{}
There are many grammar errors, please check it carefully
\re We have carefully reviewed and corrected all identified grammar issues, as well as others not explicitly mentioned. The revised manuscript has undergone thorough proofreading to ensure clarity and grammatical accuracy.

\end{cmt}

%%%%%%%%%%%%% Comment 2.4
\begin{cmt}{}{}
In Definition 1, is reasonable to say ``any potential deviations''?
\re We believe that this phrase is reasonable and essential to the definition and intention of security against plan-deviation attacks. The definition is designed to ensure that the trajectory plan accounts for all possible paths a compromised robot might take toward forbidden regions. By explicitly requiring that any such deviation results in the robot missing its next co-observation, the definition provides a rigorous and comprehensive security guarantee. As such, the phrase "any potential deviations" accurately reflects the intended scope of the definition.
\end{cmt}

\begin{cmt}{}{}
	In the definition of $U$, what does ``,'' mean?
	\re  We are not entirely sure what the specific concern or issue is in this context. However, if the reviewer is referring to $u'$ , it was intended to denote the vector $u$ before normalization. To avoid any potential confusion, we have revised the notation in the updated manuscript. We appreciate your feedback and have taken steps to ensure clarity in this definition.
\end{cmt}
\setcounter{definition}{8}
\setcounter{equation}{41}
\rv {\news \begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
	% \begin{equation}
	%   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
	% \end{equation}
  the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
	\begin{equation}\label{eq:H definition}
	  H(\nu_1,\nu_2) = 2 u u\transpose-I.
	\end{equation}
  \end{definition}}
\begin{cmt}{}{}
	How to solve (9a)?
	\re  In practical applications, Eq.4a (originally 9a) is solved iteratively using a nonlinear optimization solver, such as \emph{fmincon}. Additionally, the derivatives of the constraint projection functions, as derived later in the manuscript, are specifically utilized to solve the optimization problem more efficiently and quickly. These derivatives enhance the solver's performance by providing necessary gradient information, improving convergence speed. We have clarified these points in the revised manuscript to provide further insight into the solution process.
\end{cmt}
\rv {\news
\setcounter{remark}{0}
\begin{remark}
In practical application, (4a) is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} [30]. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numerical differentiation). At the same time, (4b) and (4c) have closed form solutions.
\end{remark}
[30] The MathWorks, Inc., MATLAB Optimization Toolbox, The Math- Works, Inc., Natick, Massachusetts, 2024, version R2024b, https://www. mathworks.com/products/optimization.html.
}
\begin{cmt}{}{}
	How to define $d_{\max}$ in (14)?
	\re $d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.
\end{cmt}
\setcounter{constraint}{0}
\setcounter{equation}{6}
\rv \begin{constraint}[Co-observation constraint]\label{constraint:coobservation}
	\begin{align}
	D(\vq) &= \overrightarrow{q_{aj}q_{bj}}, \label{eq:coobservation_constraint}\\
	  \sZ &= \{\vz \mid \norm{\vz} \leq d_{max} \},\\
	   \Pi_\sZ(z) & = \begin{cases}
	d_{max}\frac{\vz}{\norm{\vz}} &\text{if } \norm{\vz} > d_{max},\\
	\vz	& otherwise,
	\end{cases}
	\end{align}
	where $a,b$ are the indices of the pair of agents required for a mutual inspection, \new{$d_{max}$ is the maximum distance between a pair of robots that the secure can be ensured through co-observation.}
	\end{constraint}

@@

\begin{cmt}{}{}
	In Definition 4, it is unclear that $\mathcal E$ is an ellipsoid. There is no definition of the function $d(\cdot,\cdot)$;
	\re In the revised manuscript, we have added additional explanations to clarify that $\cE$ is an ellipsoid and to explicitly define the function $d(\cdot,\cdot)$ to avoid confusion and ensure clarity.
\end{cmt}
\rv {\news \setcounter{definition}{1}
\begin{definition}\label{sec:ellipsoidal definition}
Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
\end{definition}

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }

\begin{cmt}{}{}
	It is unclear about how to ensure the security. Where is the attack?
	\re We have added a detailed description of the attacker model in the revised manuscript, outlining how a compromised robot attempts to gain unauthorized access while masquerading as legitimate. The mechanisms for ensuring security are formally described in Definition 1 and further extended in Definition 4 and Remark 2, which outline the requirements and constraints necessary to detect and mitigate such attacks effectively. We also add potential attacks to the unsecured and secured result figures.
\end{cmt}
\rv 
\textbf{In Section I, Introduction, Paragraph 1, we revised}

{\news A countermeasure to these \emph{plan-deviation attacks} [2]–[4] is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior. These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}

\textbf{In Section II, after Example 1 we revised:}
\setcounter{figure}{1}
\begin{figure}[H]
	\centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
  \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
  % \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
\end{figure}
{\news 
Ideally, robots are expected to spread out in a Boustrophedon pattern to efficiently explore the task space, optimize coverage, and minimize reconstruction uncertainty (\cref{fig:SecurityBreak}). However, we consider the possibility of threats following the \emph{physical masquerade attack} model [2], where a compromised insider (robot) masquerading as a properly functioning agent, attempts to gain access to unauthorized locations without detection. The attacker leverages full knowledge of the motion plan and exploits the compromised robot to provide false self-reports to the central entity (CE). These malicious deviations remain undetected as long as observations from uncompromised robots align with the motion plan. The corresponding security requirement can then be formally defined as:}
\setcounter{definition}{0}
\begin{definition}\label{def:secured-plan}
  A multi-robot trajectory plan is \new{secured against} plan-deviation attacks if it \new{ensures} that any potential deviations to these forbidden regions will cause the corresponding robot to miss their next co-observation with other robots. 
\end{definition}
\setcounter{definition}{3}
\setcounter{remark}{1}

\textbf{In section II.C:}

### 2024-12-12 response.tex

{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$. \cref{def:secured-plan} can then be restated as follows:
\begin{definition}\label{rmk:revised-security}
  A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}
}
\setcounter{figure}{3}
\begin{figure}[H]
	\centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
  \caption{{\news Trajectory design of a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints. Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
  \label{fig:example-application}
  \end{figure}

\textbf{In Section III.A:}

{\news To ensure the security of the reference trajectory, the reachability region between consecutive checkpoints must avoid intersections with forbidden regions. This requirement can be formally stated as:
\begin{remark}\label{rmk:checkpoints}
  A set of checkpoints $V_{p}=\{ v_{p0}, \dots ,v_{pT}\}$ (arranged in ascending order of $t_{v_{pi}}$) can secure the reference trajectory for sub-team $p$, if $\mathcal{E}(q_{v_{pi}}, q_{v_{p(i+1)}}, t_{v_{pi}},t_{v_{p(i+1)}}) \intersect F = \emptyset$ for every $i$, where $F$ is the union of all forbidden regions.
  \end{remark}
}

\begin{cmt}{}{}
	Please check the reference format carefully.
	\re Thank you for pointing this out. We have carefully reviewed and revised the reference format in the manuscript to ensure consistency and compliance with the journal's guidelines.
\end{cmt}
\newpage
\section{Response to reviewer 3} 
\begin{cmt}{}
	Please check the grammar and typos, here are some within the first two pages:
	\dots
	I stop marking these typos after page 2, but please do a careful proof-read of your own paper. 
	\re  We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism. In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions. We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.
\end{cmt}
\begin{cmt}{}{}
	Some definitions and symbols are not clearly explained:
	1) First paragraph of Sec 2: the dimension of $q$ should be $n_p*m*T$
	right? Further, how is it aggregated? In what order?	
	\re In the revised manuscript, we have clarified that the dimension of $q$ have been clearified and have further explained the aggregation process.
\end{cmt}
\rv \textbf{In Section II, we modified:}

{\news We denote the trajectory as $\vq_i = [q_{i0}\dots q_{iT}]\in\real{m\times T}$, where $q_{ij}\in\real{m}$ is the waypoint of agent $i$ in a $m$ dimensional state space, $T$ is the time horizon. For a total of $n_p$ robots, trajectories can be represented as an aggregated vector $\vq = \stack(\vq_1,\dots,\vq_{n_p})\in \real{m n_p\times T}$, where $\stack(\cdot)$ denotes the vertical stacking operation. }
\begin{cmt}{}{}
	Def 2: what is $\hat v_F$ and $\hat v_\epsilon$? Also $v_F$ and $v_e$ are defined later, so not proper to use here. 
	\re We acknowledge that in Definition 2 (Definition 9 in the revised manuscript) $\hat v_F$ and $\hat v_\epsilon$ were typographical errors and have been corrected in the revised manuscript. Additionally, the terms $v_F$ and $v_e$ have been modified to ensure proper introduction and to avoid confusion.
\end{cmt}
\setcounter{definition}{8}
\setcounter{equation}{41}
\rv 
{\news 
\begin{definition} Let $\nu_1$ and $\nu_2$ be two unitary vectors ($\norm{\nu_1}=\norm{\nu_2}=1$). Define the normalized vector $u = \frac{\nu_1+\nu_2}{\norm{\nu_1+\nu_2}}$,
	% \begin{equation}
	%   u=\nu_1+\nu_2,\quad u =\frac{u'}{\norm{u'}}.
	% \end{equation}
  the \emph{Householder rotation} $H(\nu_1,\nu_2)$ is defined as
	\begin{equation}\label{eq:H definition}
	  H(\nu_1,\nu_2) = 2 u u\transpose-I.
	\end{equation}
  \end{definition}}

  \begin{cmt}{}{}
	3) What is the difference between lowercase letters and bold-type
lowercase letters? If bold-type denotes vectors, then why $x(t)$ in
eq(2), u, v's in eq (3) not in bold-type?  
\re We apologize for the confusion regarding the notation. To address this, we have added additional clarification in the revised manuscript. Specifically, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, while bold symbols represent aggregated states of a single robot or multiple robots (e.g., $\vq$). This distinction has been made explicit to avoid further ambiguity.
  \end{cmt}
  \rv {\news 
  \noindent\myparagraph{Notation} 
  In this paper, we use non-bold symbols to denote single-agent states (e.g. $q_{ij}$) and scalars, and bold symbols to represent aggregated states of single robot and multiple robots (e.g. $\vq$). }

@@

  \begin{cmt}{}{}
3)	Def 3: the 'workspace' is not specified before. The function
d(q1,q2) is not defined. Further, this def is confusing, do you want to
say that the reachability region is the union of all trajectory states,
such that starting from q(t1) = q1, you are able to reach q(t2) = q2
while satisfying the speed constraints?

4) Def 4: what is $v_{maq}$? Why is the ellipsoid an
over-approximation of reachability region? 
\re Thank you for pointing out the issues on Definition 3 (Definition 2 in the new manuscript). In the revised manuscript, we have modified the term 'workspace' for clarity, refined the definition to avoid confusion, and added a detailed description of the function $ d(q_1, q_2)$, which represents the Euclidean distance between $q_1$  and  $q_2$ . These changes aim to ensure the definition accurately conveys that the reachability region is the union of all trajectory states satisfying the specified conditions.

As for Defnintion 4 (Definition 3 in the new manuscript), we acknowledge that the term $v_{maq}$ as a typographical error, and it has been corrected to $v_{max}$ in the revised manuscript. Additionally, we have provided a more detailed explanation to clarify why the ellipsoid is an over-approximation of the reachability region. Specifically, it represents the set of points $q'$ whose sum of distances two foci $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid.
  \end{cmt}
  \setcounter{definition}{1}
  \rv {\news
  \begin{definition}\label{sec:ellipsoidal definition}
  Consider a robot $i$ starting from $q_{1}$ at time $t_1$ and reaching $q_{2}$ at time $t_2$. The \emph{reachability region} between $t_1$ and $t_2$ is defined as the set of points $q'$ in the free configuration space for which there exists a kinematically feasible trajectory containing $q'$.
  \end{definition}

  For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):
  \begin{definition}\label{def:Reachability}
	  The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
  \end{definition}
  This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where $a$ is the major radius of the ellipsoid. }

  \begin{cmt}{}{}
	 Fig 3: legends are too small. 
	\re We acknowledge that the legends and other aspects of the figures in the original manuscript were not clear. In the revised manuscript, we have addressed these issues by replotting the figures, including Figure 3, to ensure readability and clarity.
  \end{cmt}
  \rv \setcounter{figure}{1}
  \begin{figure}[H]
	\centering
	\subfloat[\new{Map exploration task}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth,, trim = 0.3cm 1.3cm 0.3cm 2cm,valign=c]{illustration figure_1}} 
	\subfloat[Continuous world trajectory\label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth, trim = 0.3cm 1.3cm 0.3cm 2cm, valign=c]{SecurityBreak_v3}}
	% \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
	\caption{\new{(\ref{fig:illustration}) Illustration of a 3 robot map exploration task case. (\ref{fig:SecurityBreak}) The unsecured trajectory design optimized for a map exploration task. Potential security breaches, indicated by red dashed lines, highlight paths that could allow unauthorized access to forbidden regions.}}
  \end{figure}
  \setcounter{figure}{3}
  \begin{figure}[H]
	\centering
	% \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
	\subfloat[\new{Grid world result}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
	% \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
	\subfloat[Secured result. \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
	\caption{{\news Trajectory design of a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints. Attack attempts into the forbidden region (red dashed line) will cause team 1 miss the next scheduled co-observation.}}
	\label{fig:example-application}
  \end{figure}
  \begin{cmt}{}{}
	4. The idea of the reachability ellipse seems very similar to another
idea called 'safe flight corridor' from
 "Liu, Sikang, et al. "Planning dynamically feasible trajectories for
quadrotors using safe flight corridors in 3-d complex environments."
IEEE Robotics and Automation Letters 2.3 (2017): 1688-1695." 
What is this essential difference between these two methods? 
\re Thank you for highlighting the potential similarity between the reachability ellipse and the Safe Flight Corridor (SFC) method. Our approach differs fundamentally in its purpose and application. Unlike the ellipsoids in IRIS and SFC, which are designed to approximate collision-free spaces, the reachability region in our method explicitly maps all reachable states given several known states (and regardless of collision) and is tailored to address security concerns.
